Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
praise GitHub for making collaboration easy

Started in 2009, \sklearn is developed by an international team
of several dozen volunteers, mostly researchers from various fields
(e.g., machine learning, natural language processing, or neuroscience).
The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features.
Finally, additions to the code base must pass code review
by at least two developers not involved in the implementation
of the proposed addition.

>>>>

Started in 2009, \sklearn is developed by an international team
of several dozen volunteers, mostly researchers from various fields
(e.g., machine learning, natural language processing, or neuroscience).
The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Development proceeds on GitHub (\url{https://github.com/scikit-learn}),
a platform which greatly facilitates this kind of collaboration.
Because of the large number of developers,
particular emphasis is put on keeping the project maintainable.
In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features.
Finally, additions to the code base must pass code review
by at least two developers not involved in the implementation
of the proposed addition.
